---
title: "Part I -- Severe Weather Reports"
author: "Dr. Zoe Searcy"
date: "2026-04-13"
output: html_document
---

```{r}
library(sf)
library(dplyr)
library(lubridate)
library(tmap)
library(USAboundaries)
```


## Tornado Data

```{r, eval = FALSE}
torn.df <- as.data.frame(st_read("C:/Users/SCHRODEZ/OneDrive - Embry-Riddle Aeronautical University/Desktop/Research_Projects/SevereWX_ssp585/1950-2024-torn-initpoint/1950-2024-torn-initpoint/1950-2024-torn-initpoint.shp"))
```

Use the rules outlined in the OneTor_F-scale-modifications.pdf (*https://www.spc.noaa.gov/wcm/OneTor_F-scale-modifications.pdf*) to assign EF ratings to any missing mag values (mag = -9).
```{r, eval = FALSE}
torn.df <- torn.df %>%
  filter(!st %in% c("AK", "PR", "HI")) %>%
  mutate(mag = ifelse(mag == -9 & len <= 5 & loss < 50, 0, mag),
         mag = ifelse(mag == -9 & len > 5 & loss < 50, 1, mag),
         mag = ifelse(mag == -9 & len <= 5 & loss < 5000, 0, mag),
         mag = ifelse(mag == -9 & len > 5 & loss < 5000, 2, mag),
         mag = ifelse(mag == -9 & len <= 5 & loss < 500000, 1, mag),
         mag = ifelse(mag == -9 & len > 5 & loss < 500000, 3, mag),
         mag = ifelse(mag == -9 & len <= 5 & loss < 50000000, 2, mag),
         mag = ifelse(mag == -9 & len > 5 & loss < 50000000, 4, mag),
         mag = ifelse(mag == -9 & len <= 5 & loss < 5000000000, 3, mag),
         mag = ifelse(mag == -9 & len > 5 & loss < 5000000000, 5, mag))
```


```{r, eval = FALSE}
torn.df <- torn.df %>%
  filter(yr >= 1980, #keeping with Chiara Lepore's methodology
         mag >= 1) #remove reporting bias found with the EF0 reports
```

```{r, eval = FALSE}
test <- torn.df %>%
  mutate(dy = format(as.Date(date,format="%y-%m-%d"), "%d"))
```



```{r, eval = FALSE}
torn.df <- torn.df %>%
  mutate(dy = format(as.Date(date,format="%Y-%m-%d"), "%d"),
         DateTime = as.POSIXct(paste(yr, mo, dy, time), format = "%Y%m%d%H:%M:%S"),
         Hour = hour(DateTime),
         Year = year(DateTime),
         conv_DateTime = DateTime - as.difftime(6, unit = "hours"),
         conv_Date = as.Date(as_datetime(ifelse(Hour < 6, (DateTime - 86400), conv_DateTime), tz = "EST")),
         length_m = len * 1609.34,
         length_m = ifelse(length_m == 0, min(length_m[length_m > 0]), length_m), #takes care of zero length
         width_m = wid * .9144,
         width_m = ifelse(width_m == 0, min(width_m[width_m > 0]), width_m), #takes care of zero width
         width_m = ifelse(Year >= 1995, width_m * pi/4, width_m), #takes care of change: avg to max
         cas = inj + fat,
         AreaPath = length_m * width_m,
         Ma = factor(month.abb[mo], levels = month.abb[1:12])) %>%
  sf::st_sf()
```

## Hail Data

```{r, eval = FALSE}
hail.df <- as.data.frame(st_read("C:/Users/SCHRODEZ/OneDrive - Embry-Riddle Aeronautical University/Desktop/Research_Projects/SevereWX_ssp585/1955-2024-hail-initpoint/1955-2024-hail-initpoint/1955-2024-hail-initpoint.shp"))
```

```{r}
hail.df <- hail.df %>%
  filter(yr >= 1980, #keeping with Chiara Lepore's methodology
         mag >= 1.0) #keep only "severe" reports of 1 inch or greater
```

```{r, eval = FALSE}
hail.df <- hail.df %>%
  mutate(dy = format(as.Date(date,format="%Y-%m-%d"), "%d"),
         DateTime = as.POSIXct(paste(yr, mo, dy, time), format = "%Y%m%d%H:%M:%S"),
         Hour = hour(DateTime),
         Year = year(DateTime),
         conv_DateTime = DateTime - as.difftime(6, unit = "hours"),
         conv_Date = as.Date(as_datetime(ifelse(Hour < 6, (DateTime - 86400), conv_DateTime), tz = "EST")),
         cas = inj + fat,
         Ma = factor(month.abb[mo], levels = month.abb[1:12])) %>%
  sf::st_sf()
```

```{r, eval = FALSE}
#save(torn.df, hail.df, file = "SVR_WX_Reports.RData")
```

## Wind Data: 

```{r, eval = FALSE}
wind.df <- as.data.frame(st_read("C:/Users/SCHRODEZ/OneDrive - Embry-Riddle Aeronautical University/Desktop/Research_Projects/SevereWX_ssp585/1955-2024-wind-initpoint/1955-2024-wind-initpoint/1955-2024-wind-initpoint.shp"))
```
```{r}
wind.df <- wind.df %>%
  filter(yr >= 1980, #keeping with Chiara Lepore's methodology
         mag >= 50) #keep only "severe" reports of 50 kts or greater
```


```{r, eval = FALSE}
wind.df <- wind.df %>%
  mutate(dy = format(as.Date(date,format="%Y-%m-%d"), "%d"),
         DateTime = as.POSIXct(paste(yr, mo, dy, time), format = "%Y%m%d%H:%M:%S"),
         Hour = hour(DateTime),
         Year = year(DateTime),
         conv_DateTime = DateTime - as.difftime(6, unit = "hours"),
         conv_Date = as.Date(as_datetime(ifelse(Hour < 6, (DateTime - 86400), conv_DateTime), tz = "EST")),
         cas = inj + fat,
         Ma = factor(month.abb[mo], levels = month.abb[1:12])) %>%
  sf::st_sf()
```

```{r, eval = FALSE}
#save(torn.df, hail.df, wind.df, file = "SVR_WX_Reports.RData")
```


## Count the tornado, wind, and hail reports per county and per state:

We are going to remove Alaska and Hawaii from the data. Bring the focus to the lower 48 states.
```{r, eval = FALSE}
sts <- state.name[!state.name %in% c("Alaska", "Hawaii")]
stateBorders <- us_states(states = sts)
countyBorders <- us_counties(states = sts)
```

Make these data frames simple features objects.
```{r, eval = FALSE}
stateBorders <- st_as_sf(stateBorders)
countyBorders <- st_as_sf(countyBorders)
```

```{r, eval = FALSE}
tm_shape(stateBorders) + 
   tm_fill(fill = "white", fill_alpha = 0.75)+ 
  tm_borders(col = "black") +
tm_shape(countyBorders) + 
  tm_borders(col = "gray70", fill_alpha = 0.1) +
  tm_compass(size = 3, 
             fontsize = 1, 
             color.dark = "gray70",
             position = c("left", "bottom")) +   
  tm_scalebar(text.size = 0.8, 
              lwd = 3, 
              color.dark = "gray70",
             position = c("left", "bottom")) +
   tm_layout(legend.frame = FALSE,
            inner.margins = c(.05, .05, .05, .05), #S, W, N, E
            legend.bg.color = "white", legend.text.size = .5)
```

```{r, eval = FALSE}
#Make sure they have the same CRS
countyBorders<- st_transform(countyBorders,  
                            crs = st_crs(torn.df))

# Count the number of tornadoes in each county
gI_T <- st_intersects(torn.df, countyBorders, sparse = FALSE)
gI_W <- st_intersects(wind.df, countyBorders, sparse = FALSE)
gI_H <- st_intersects(hail.df, countyBorders, sparse = FALSE)

# Change the column names
colnames(gI_T) <- countyBorders$name
colnames(gI_W) <- countyBorders$name
colnames(gI_H) <- countyBorders$name

# Add a new column to the counties data
countyBorders$numTorn <- colSums(gI_T)
countyBorders$numSVRhail <- colSums(gI_H)
countyBorders$numSVRwind <- colSums(gI_W)
```

```{r, eval = FALSE}
#Make sure they have the same CRS
stateBorders<- st_transform(stateBorders,  
                            crs = st_crs(torn.df))

# Count the number of tornadoes in each county
gI_T <- st_intersects(torn.df, stateBorders, sparse = FALSE)
gI_W <- st_intersects(wind.df, stateBorders, sparse = FALSE)
gI_H <- st_intersects(hail.df, stateBorders, sparse = FALSE)

# Change the column names
colnames(gI_T) <- stateBorders$name
colnames(gI_W) <- stateBorders$name
colnames(gI_H) <- stateBorders$name

# Add a new column to the counties data
stateBorders$numTorn <- colSums(gI_T)
stateBorders$numSVRhail <- colSums(gI_H)
stateBorders$numSVRwind <- colSums(gI_W)
```

```{r, eval = FALSE}
#save(torn.df, hail.df, wind.df, stateBorders, countyBorders, file = "SVR_WX_Reports.RData")
```

## Making Maps
```{r}
load("SVR_WX_Reports.RData")
```


```{r}
countytorns <- tm_shape(stateBorders) + 
   tm_fill(fill = "white", fill_alpha = 0.75)+ 
  tm_borders(col = "black") +
  tm_compass(size = 3, 
             fontsize = 1, 
             color.dark = "gray70",
             position = c("left", "bottom")) +   
  tm_scalebar(text.size = 0.8, 
              lwd = 3, 
              color.dark = "gray70",
             position = c("left", "bottom")) +
   tm_layout(legend.frame = FALSE,
            inner.margins = c(.05, .05, .05, .05), #S, W, N, E
            legend.bg.color = "white", legend.text.size = .5) +
tm_shape(countyBorders) + 
  tm_polygons(fill = "numTorn", col = "gray50",
              tm_scale_intervals(n = 7, # Number of classes you wan
                                 style = "fixed",
                                 breaks = c(0,1, 10, 20, 40, 80, 90), 
                                 labels = c("0", "1 to 9", "10 to 19", "20 to 39", "40 to 79", "> 80"),
                                 values = "brewer.reds"),
              fill.legend = tm_legend(title = "Total Tornadoes", 
                                  orientation = "portrait", 
                                  legend.bg.color = "white", 
                                  legend.text.size = .5,
                                  position = tm_pos_in("right", "bottom"))) 
```

```{r}
countyhail <- tm_shape(stateBorders) + 
   tm_fill(fill = "white", fill_alpha = 0.75)+ 
  tm_borders(col = "black") +
  tm_compass(size = 3, 
             fontsize = 1, 
             color.dark = "gray70",
             position = c("left", "bottom")) +   
  tm_scalebar(text.size = 0.8, 
              lwd = 3, 
              color.dark = "gray70",
             position = c("left", "bottom")) +
   tm_layout(legend.frame = FALSE,
            inner.margins = c(.05, .05, .05, .05), #S, W, N, E
            legend.bg.color = "white", legend.text.size = .5) +
tm_shape(countyBorders) + 
  tm_polygons(fill = "numSVRhail", col = "gray50",
              tm_scale_intervals(n = 7, # Number of classes you wan
                                 style = "fixed",
                                 breaks = c(0,1, 25, 50, 100, 200, 500, 1000,1500), 
                                 labels = c("0", "1 to 24", "25 to 49", "50 to 99", "100 to 199", "200 to 499", "500 to 999", "> 1000"),
                                 values = "brewer.greens"),
              fill.legend = tm_legend(title = "Total Tornadoes", 
                                  orientation = "portrait", 
                                  legend.bg.color = "white", 
                                  legend.text.size = .5,
                                  position = tm_pos_in("right", "bottom"))) 
```

```{r}
countywind <- tm_shape(stateBorders) + 
   tm_fill(fill = "white", fill_alpha = 0.75)+ 
  tm_borders(col = "black") +
  tm_compass(size = 3, 
             fontsize = 1, 
             color.dark = "gray70",
             position = c("left", "bottom")) +   
  tm_scalebar(text.size = 0.8, 
              lwd = 3, 
              color.dark = "gray70",
             position = c("left", "bottom")) +
   tm_layout(legend.frame = FALSE,
            inner.margins = c(.05, .05, .05, .05), #S, W, N, E
            legend.bg.color = "white", legend.text.size = .5) +
tm_shape(countyBorders) + 
  tm_polygons(fill = "numSVRwind", col = "gray50",
              tm_scale_intervals(n = 7, # Number of classes you wan
                                 style = "fixed",
                                 breaks = c(0,1, 25, 50, 100, 200, 500, 1000,1500), 
                                 labels = c("0", "1 to 24", "25 to 49", "50 to 99", "100 to 199", "200 to 499", "500 to 999", "> 1000"),
                                 values = "brewer.blues"),
              fill.legend = tm_legend(title = "Total Tornadoes", 
                                  orientation = "portrait", 
                                  legend.bg.color = "white", 
                                  legend.text.size = .5,
                                  position = tm_pos_in("right", "bottom"))) 
```

```{r}
tmap_arrange(countytorns, countyhail, countywind)
```

*State Level*
```{r}
tm_shape(stateBorders) + 
  tm_polygons(fill = "numTorn", col = "gray50",
              tm_scale_intervals(n = 7, # Number of classes you wan
                                 style = "fixed",
                                 breaks = c(0,1, 100, 250, 500, 1000, 1500,2500 ), 
                                 labels = c("0", "1 to 99", "100 to 249", "250 to 499", "500 to 999", "1000 to 1499",  "> 1500"),
                                 values = "brewer.reds"),
              fill.legend = tm_legend(title = "Total Tornadoes", 
                                  orientation = "portrait", 
                                  legend.bg.color = "white", 
                                  legend.text.size = .5,
                                  position = tm_pos_in("right", "bottom"))) +
  tm_compass(size = 3, 
             fontsize = 1, 
             color.dark = "gray70",
             position = c("left", "bottom")) +   
  tm_scalebar(text.size = 0.8, 
              lwd = 3, 
              color.dark = "gray70",
             position = c("left", "bottom")) +
   tm_layout(legend.frame = FALSE,
            inner.margins = c(.05, .05, .05, .05), #S, W, N, E
            legend.bg.color = "white", legend.text.size = .5)
```
