---
title: 'Part II: CMIP6 Convective Variables'
author: "Dr. Searcy"
date: "2025-12-16"
output: html_document
---

Load the required packages: 
``` {r, eval = FALSE}
library(ncdf4)
library(CFtime)

library(lattice)
```

## Open NetCDF Files
### Historical Convective Precipitation
``` {r, eval = FALSE}
ncpath <- "C:/Users/SCHRODEZ/OneDrive - Embry-Riddle Aeronautical University/Desktop/Research_Projects/TornActivity_ssp585/"
ncname <- "CP_monthly_NAmerica_historical" 
ncfname <- paste(ncpath, ncname, ".nc", sep="")
library(ncdf4)
dat_nc <- nc_open(ncfname)
```

``` {r, eval = FALSE}
varname = dat_nc$var$ta$longname
varname <- gsub(" ", "", varname)

time_stamp <- ncvar_get(dat_nc, "time")

model <- ncvar_get(dat_nc, "model")

lons <- ncvar_get(dat_nc,"lon")
lats <- ncvar_get(dat_nc,"lat")

dat_array <- ncvar_get(dat_nc, "prc")

tunits <- ncatt_get(dat_nc,"time","units")

cf <- CFtime(tunits$value, calendar = "proleptic_gregorian", time_stamp) 

timestamps <- as_timestamp(cf) # get character-string times

time_cf <- parse_timestamps(cf, timestamps) # parse the string into date components
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[1,,,]
 


dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))
x <- c(timestamps)
colnames(PRC_model1) <- c("Lon", "Lat", x)

PRC_model1 %>% pivot_longer(cols=c('Lon', 'Lat'),
                    names_to='Date',
                    values_to='prc')

modname <- model[1]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
PRC_model1 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(PRC_model1) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[2,,,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[2]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
PRC_model2 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(PRC_model2) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[3,,,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[3]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
PRC_model3 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(PRC_model3) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[4,,,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[4]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
PRC_model4 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(PRC_model4) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[5,,,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[5]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
PRC_model5 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(PRC_model5) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[6,,,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[6]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
PRC_model6 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(PRC_model6) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[7,,,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[7]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
PRC_model7 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(PRC_model7) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
PRC_historical <- rbind(PRC_model1,PRC_model2,PRC_model3,PRC_model4,PRC_model5,PRC_model6,PRC_model7)
```

###SSP 585 Convective Precipitation

``` {r, eval = FALSE}
ncpath <- "C:/Users/SCHRODEZ/OneDrive - Embry-Riddle Aeronautical University/Desktop/Research_Projects/TornActivity_ssp585/"
ncname <- "CP_monthly_NAmerica_ssp585" 
ncfname <- paste(ncpath, ncname, ".nc", sep="")
library(ncdf4)
dat_nc <- nc_open(ncfname)
```

``` {r, eval = FALSE}
varname = dat_nc$var$ta$longname
varname <- gsub(" ", "", varname)

time_stamp <- ncvar_get(dat_nc, "time")

model <- ncvar_get(dat_nc, "model")

lons <- ncvar_get(dat_nc,"lon")
lats <- ncvar_get(dat_nc,"lat")

dat_array <- ncvar_get(dat_nc, "prc")

tunits <- ncatt_get(dat_nc,"time","units")

cf <- CFtime(tunits$value, calendar = "proleptic_gregorian", time_stamp) 

timestamps <- as_timestamp(cf) # get character-string times

time_cf <- parse_timestamps(cf, timestamps) # parse the string into date components
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[1,,,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[1]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
PRC_model1 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(PRC_model1) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[2,,,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[2]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
PRC_model2 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(PRC_model2) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[3,,,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[3]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
PRC_model3 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(PRC_model3) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[4,,,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[4]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
PRC_model4 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(PRC_model4) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[5,,,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[5]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
PRC_model5 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(PRC_model5) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[6,,,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[6]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
PRC_model6 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(PRC_model6) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[7,,,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[7]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
PRC_model7 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(PRC_model7) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
PRC_ssp585 <- rbind(PRC_model1,PRC_model2,PRC_model3,PRC_model4,PRC_model5,PRC_model6,PRC_model7)
```

### SH06 Historical

``` {r, eval = FALSE}
ncpath <- "C:/Users/SCHRODEZ/OneDrive - Embry-Riddle Aeronautical University/Desktop/Research_Projects/TornActivity_ssp585/"
ncname <- "Shear_monthly_NAmerica_historical" 
ncfname <- paste(ncpath, ncname, ".nc", sep="")
library(ncdf4)
dat_nc <- nc_open(ncfname)
```

``` {r, eval = FALSE}
time_stamp <- ncvar_get(dat_nc, "time")

model <- ncvar_get(dat_nc, "model")

lons <- ncvar_get(dat_nc,"lon")
lats <- ncvar_get(dat_nc,"lat")
nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_array <- ncvar_get(dat_nc, "S06")

tunits <- ncatt_get(dat_nc,"time","units")

cf <- CFtime(tunits$value, calendar = "proleptic_gregorian", time_stamp) 

timestamps <- as_timestamp(cf) # get character-string times

time_cf <- parse_timestamps(cf, timestamps) # parse the string into date components
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,,1]

dat_long <- as.vector(dat_array2)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[1]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
S06_model1 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(S06_model1) <- c("Lon", "Lat", x, "Model")

head(S06_model1)
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,,2]

dat_long <- as.vector(dat_array2)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[2]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
S06_model2 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(S06_model2) <- c("Lon", "Lat", x, "Model")

head(S06_model2)
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,,3]

dat_long <- as.vector(dat_array2)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[3]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
S06_model3 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(S06_model3) <- c("Lon", "Lat", x, "Model")

head(S06_model3)
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,,4]

dat_long <- as.vector(dat_array2)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[4]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
S06_model4 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(S06_model4) <- c("Lon", "Lat", x, "Model")

head(S06_model4)
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,,5]

dat_long <- as.vector(dat_array2)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[5]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
S06_model5 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(S06_model5) <- c("Lon", "Lat", x, "Model")

head(S06_model5)
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,,6]

dat_long <- as.vector(dat_array2)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[6]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
S06_model6 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(S06_model6) <- c("Lon", "Lat", x, "Model")

head(S06_model6)
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,,7]

dat_long <- as.vector(dat_array2)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[7]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
S06_model7 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(S06_model7) <- c("Lon", "Lat", x, "Model")

head(S06_model7)
```

``` {r, eval = FALSE}
S06_historical <- rbind(S06_model1,S06_model2,S06_model3,S06_model4,S06_model5,S06_model6,S06_model7)
```

###SH06 ssp585


``` {r, eval = FALSE}
ncpath <- "C:/Users/SCHRODEZ/OneDrive - Embry-Riddle Aeronautical University/Desktop/Research_Projects/TornActivity_ssp585/"
ncname <- "Shear_monthly_NAmerica_ssp585" 
ncfname <- paste(ncpath, ncname, ".nc", sep="")
library(ncdf4)
dat_nc <- nc_open(ncfname)
```

``` {r, eval = FALSE}
time_stamp <- ncvar_get(dat_nc, "time")

model <- ncvar_get(dat_nc, "model")

lons <- ncvar_get(dat_nc,"lon")
lats <- ncvar_get(dat_nc,"lat")
nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_array <- ncvar_get(dat_nc, "S06")

tunits <- ncatt_get(dat_nc,"time","units")

cf <- CFtime(tunits$value, calendar = "proleptic_gregorian", time_stamp) 

timestamps <- as_timestamp(cf) # get character-string times

time_cf <- parse_timestamps(cf, timestamps) # parse the string into date components
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[1,,,]

dat_long <- as.vector(dat_array2)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[1]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
S06_model1 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(S06_model1) <- c("Lon", "Lat", x, "Model")

head(S06_model1)
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[2,,,]

dat_long <- as.vector(dat_array2)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[2]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
S06_model2 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(S06_model2) <- c("Lon", "Lat", x, "Model")

head(S06_model2)
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[3,,,]

dat_long <- as.vector(dat_array2)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[3]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
S06_model3 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(S06_model3) <- c("Lon", "Lat", x, "Model")

head(S06_model3)
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[4,,,]

dat_long <- as.vector(dat_array2)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[4]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
S06_model4 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(S06_model4) <- c("Lon", "Lat", x, "Model")

head(S06_model4)
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[5,,,]

dat_long <- as.vector(dat_array2)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[5]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
S06_model5 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(S06_model5) <- c("Lon", "Lat", x, "Model")

head(S06_model5)
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[6,,,]

dat_long <- as.vector(dat_array2)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[6]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
S06_model6 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(S06_model6) <- c("Lon", "Lat", x, "Model")

head(S06_model6)
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[7,,,]

dat_long <- as.vector(dat_array2)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[7]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
S06_model7 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(S06_model7) <- c("Lon", "Lat", x, "Model")

head(S06_model7)
```

``` {r, eval = FALSE}
S06_ssp585 <- rbind(S06_model1,S06_model2,S06_model3,S06_model4,S06_model5,S06_model6,S06_model7)
```

### Historical Convective

### CAPE ml500 historical

``` {r, eval = FALSE}
ncpath <- "C:/Users/SCHRODEZ/OneDrive - Embry-Riddle Aeronautical University/Desktop/Research_Projects/TornActivity_ssp585/"
ncname <- "Convective_monthly_NAmerica_historical" 
ncfname <- paste(ncpath, ncname, ".nc", sep="")
library(ncdf4)
dat_nc <- nc_open(ncfname)
```

``` {r, eval = FALSE}
time_stamp <- ncvar_get(dat_nc, "time")

model <- ncvar_get(dat_nc, "model")

lons <- ncvar_get(dat_nc,"lon")
lats <- ncvar_get(dat_nc,"lat")
nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_array <- ncvar_get(dat_nc, "cape_ml500")

tunits <- ncatt_get(dat_nc,"time","units")

cf <- CFtime(tunits$value, calendar = "proleptic_gregorian", time_stamp) 

timestamps <- as_timestamp(cf) # get character-string times

time_cf <- parse_timestamps(cf, timestamps) # parse the string into date components
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,1,]

dat_long <- as.vector(dat_array2)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[1]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
CAPE_ml500_model1 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(CAPE_ml500_model1) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,2,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[2]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
CAPE_ml500_model2 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(CAPE_ml500_model2) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,3,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[3]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
CAPE_ml500_model3 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(CAPE_ml500_model3) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,4,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[4]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
CAPE_ml500_model4 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(CAPE_ml500_model4) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,5,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[5]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
CAPE_ml500_model5 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(CAPE_ml500_model5) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,6,]

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[6]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
CAPE_ml500_model6 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(CAPE_ml500_model6) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,7,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[7]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
CAPE_ml500_model7 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(CAPE_ml500_model7) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
CAPE_ml500_historical <- rbind(CAPE_ml500_model1,CAPE_ml500_model2,CAPE_ml500_model3,CAPE_ml500_model4,CAPE_ml500_model5,CAPE_ml500_model6,CAPE_ml500_model7)
```

CAPE_s


``` {r, eval = FALSE}
dat_array <- ncvar_get(dat_nc, "cape_s")

dat_array2 <- dat_array[,,1,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[1]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
CAPE_s_model1 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(CAPE_s_model1) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,2,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[2]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
CAPE_s_model2 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(CAPE_s_model2) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,3,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[3]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
CAPE_s_model3 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(CAPE_s_model3) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,4,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[4]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
CAPE_s_model4 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(CAPE_s_model4) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,5,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[5]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
CAPE_s_model5 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(CAPE_s_model5) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,6,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[6]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
CAPE_s_model6 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(CAPE_s_model6) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,7,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[7]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
CAPE_s_model7 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(CAPE_s_model7) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
CAPE_s_historical <- rbind(CAPE_s_model1,CAPE_s_model2,CAPE_s_model3,CAPE_s_model4,CAPE_s_model5,CAPE_s_model6,CAPE_s_model7)
```

CIN ML500


``` {r, eval = FALSE}
dat_array <- ncvar_get(dat_nc, "cin_ml500")

dat_array2 <- dat_array[,,1,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[1]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
cin_ml500_model1 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(cin_ml500_model1) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,2,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[2]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
cin_ml500_model2 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(cin_ml500_model2) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,3,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[3]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
cin_ml500_model3 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(cin_ml500_model3) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,4,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[4]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
cin_ml500_model4 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(cin_ml500_model4) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,5,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[5]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
cin_ml500_model5 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(cin_ml500_model5) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,6,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[6]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
cin_ml500_model6 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(cin_ml500_model6) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,7,]

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[7]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
cin_ml500_model7 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(cin_ml500_model7) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
cin_ml500_historical <- rbind(cin_ml500_model1,cin_ml500_model2,cin_ml500_model3,cin_ml500_model4,cin_ml500_model5,cin_ml500_model6,cin_ml500_model7)
```

cin_s


``` {r, eval = FALSE}
dat_array <- ncvar_get(dat_nc, "cin_s")

dat_array2 <- dat_array[,,1,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[1]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
cin_s_model1 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(cin_s_model1) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,2,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[2]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
cin_s_model2 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(cin_s_model2) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,3,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[3]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
cin_s_model3 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(cin_s_model3) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,4,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[4]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
cin_s_model4 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(cin_s_model4) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,5,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[5]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
cin_s_model5 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(cin_s_model5) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,6,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[6]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
cin_s_model6 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(cin_s_model6) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,7,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[7]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
cin_s_model7 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(cin_s_model7) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
cin_s_historical <- rbind(cin_s_model1,cin_s_model2,cin_s_model3,cin_s_model4,cin_s_model5,cin_s_model6,cin_s_model7)
```

srh_lm1km


``` {r, eval = FALSE}
dat_array <- ncvar_get(dat_nc, "srh_lm1km")

dat_array2 <- dat_array[,,1,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[1]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_lm1km_model1 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_lm1km_model1) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,2,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[2]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_lm1km_model2 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_lm1km_model2) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,3,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[3]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_lm1km_model3 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_lm1km_model3) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,4,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[4]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_lm1km_model4 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_lm1km_model4) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,5,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[5]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_lm1km_model5 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_lm1km_model5) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,6,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[6]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_lm1km_model6 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_lm1km_model6) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,7,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[7]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_lm1km_model7 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_lm1km_model7) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
srh_lm1km_historical <- rbind(srh_lm1km_model1,srh_lm1km_model2,srh_lm1km_model3,srh_lm1km_model4,srh_lm1km_model5,srh_lm1km_model6,srh_lm1km_model7)
```

srh_lm3km


``` {r, eval = FALSE}
dat_array <- ncvar_get(dat_nc, "srh_lm3km")

dat_array2 <- dat_array[,,1,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[1]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_lm3km_model1 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_lm3km_model1) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,2,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[2]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_lm3km_model2 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_lm3km_model2) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,3,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[3]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_lm3km_model3 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_lm3km_model3) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,4,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[4]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_lm3km_model4 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_lm3km_model4) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,5,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[5]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_lm3km_model5 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_lm3km_model5) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,6,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[6]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_lm3km_model6 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_lm3km_model6) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,7,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[7]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_lm3km_model7 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_lm3km_model7) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
srh_lm3km_historical <- rbind(srh_lm3km_model1,srh_lm3km_model2,srh_lm3km_model3,srh_lm3km_model4,srh_lm3km_model5,srh_lm3km_model6,srh_lm3km_model7)
```

srh_rm3km


``` {r, eval = FALSE}
dat_array <- ncvar_get(dat_nc, "srh_rm3km")

dat_array2 <- dat_array[,,1,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[1]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_rm3km_model1 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_rm3km_model1) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,2,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[2]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_rm3km_model2 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_rm3km_model2) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,3,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[3]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_rm3km_model3 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_rm3km_model3) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,4,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[4]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_rm3km_model4 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_rm3km_model4) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,5,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[5]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_rm3km_model5 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_rm3km_model5) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,6,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[6]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_rm3km_model6 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_rm3km_model6) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,7,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[7]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_rm3km_model7 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_rm3km_model7) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
srh_rm3km_historical <- rbind(srh_rm3km_model1,srh_rm3km_model2,srh_rm3km_model3,srh_rm3km_model4,srh_rm3km_model5,srh_rm3km_model6,srh_rm3km_model7)
```

srh_rm1km


``` {r, eval = FALSE}
dat_array <- ncvar_get(dat_nc, "srh_rm1km")

dat_array2 <- dat_array[,,1,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[1]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_rm1km_model1 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_rm1km_model1) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,2,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[2]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_rm1km_model2 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_rm1km_model2) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,3,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[3]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_rm1km_model3 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_rm1km_model3) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,4,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[4]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_rm1km_model4 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_rm1km_model4) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,5,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[5]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_rm1km_model5 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_rm1km_model5) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,6,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[6]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_rm1km_model6 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_rm1km_model6) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,7,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[7]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_rm1km_model7 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_rm1km_model7) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
srh_rm1km_historical <- rbind(srh_rm1km_model1,srh_rm1km_model2,srh_rm1km_model3,srh_rm1km_model4,srh_rm1km_model5,srh_rm1km_model6,srh_rm1km_model7)
```

### SSP 585 Convective

### CAPE ml500 SSP585

``` {r, eval = FALSE}
ncpath <- "C:/Users/SCHRODEZ/OneDrive - Embry-Riddle Aeronautical University/Desktop/Research_Projects/TornActivity_ssp585/"
ncname <- "Convective_monthly_NAmerica_ssp585" 
ncfname <- paste(ncpath, ncname, ".nc", sep="")
library(ncdf4)
dat_nc <- nc_open(ncfname)
```

``` {r, eval = FALSE}
time_stamp <- ncvar_get(dat_nc, "time")

model <- ncvar_get(dat_nc, "model")

lons <- ncvar_get(dat_nc,"lon")
lats <- ncvar_get(dat_nc,"lat")
nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_array <- ncvar_get(dat_nc, "cape_ml500")

tunits <- ncatt_get(dat_nc,"time","units")

cf <- CFtime(tunits$value, calendar = "proleptic_gregorian", time_stamp) 

timestamps <- as_timestamp(cf) # get character-string times

time_cf <- parse_timestamps(cf, timestamps) # parse the string into date components
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,1,]

dat_long <- as.vector(dat_array2)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[1]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
CAPE_ml500_model1 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(CAPE_ml500_model1) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,2,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[2]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
CAPE_ml500_model2 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(CAPE_ml500_model2) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,3,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[3]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
CAPE_ml500_model3 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(CAPE_ml500_model3) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,4,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[4]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
CAPE_ml500_model4 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(CAPE_ml500_model4) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,5,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[5]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
CAPE_ml500_model5 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(CAPE_ml500_model5) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,6,]

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[6]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
CAPE_ml500_model6 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(CAPE_ml500_model6) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,7,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[7]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
CAPE_ml500_model7 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(CAPE_ml500_model7) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
CAPE_ml500_ssp585 <- rbind(CAPE_ml500_model1,CAPE_ml500_model2,CAPE_ml500_model3,CAPE_ml500_model4,CAPE_ml500_model5,CAPE_ml500_model6,CAPE_ml500_model7)
```

CAPE_s


``` {r, eval = FALSE}
dat_array <- ncvar_get(dat_nc, "cape_s")

dat_array2 <- dat_array[,,1,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[1]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
CAPE_s_model1 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(CAPE_s_model1) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,2,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[2]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
CAPE_s_model2 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(CAPE_s_model2) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,3,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[3]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
CAPE_s_model3 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(CAPE_s_model3) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,4,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[4]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
CAPE_s_model4 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(CAPE_s_model4) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,5,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[5]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
CAPE_s_model5 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(CAPE_s_model5) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,6,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[6]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
CAPE_s_model6 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(CAPE_s_model6) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,7,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[7]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
CAPE_s_model7 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(CAPE_s_model7) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
CAPE_s_ssp585 <- rbind(CAPE_s_model1,CAPE_s_model2,CAPE_s_model3,CAPE_s_model4,CAPE_s_model5,CAPE_s_model6,CAPE_s_model7)
```

CIN ML500


``` {r, eval = FALSE}
dat_array <- ncvar_get(dat_nc, "cin_ml500")

dat_array2 <- dat_array[,,1,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[1]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
cin_ml500_model1 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(cin_ml500_model1) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,2,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[2]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
cin_ml500_model2 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(cin_ml500_model2) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,3,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[3]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
cin_ml500_model3 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(cin_ml500_model3) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,4,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[4]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
cin_ml500_model4 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(cin_ml500_model4) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,5,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[5]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
cin_ml500_model5 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(cin_ml500_model5) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,6,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[6]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
cin_ml500_model6 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(cin_ml500_model6) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,7,]

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[7]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
cin_ml500_model7 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(cin_ml500_model7) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
cin_ml500_ssp585 <- rbind(cin_ml500_model1,cin_ml500_model2,cin_ml500_model3,cin_ml500_model4,cin_ml500_model5,cin_ml500_model6,cin_ml500_model7)
```

cin_s


``` {r, eval = FALSE}
dat_array <- ncvar_get(dat_nc, "cin_s")

dat_array2 <- dat_array[,,1,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[1]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
cin_s_model1 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(cin_s_model1) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,2,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[2]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
cin_s_model2 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(cin_s_model2) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,3,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[3]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
cin_s_model3 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(cin_s_model3) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,4,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[4]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
cin_s_model4 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(cin_s_model4) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,5,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[5]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
cin_s_model5 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(cin_s_model5) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,6,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[6]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
cin_s_model6 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(cin_s_model6) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,7,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[7]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
cin_s_model7 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(cin_s_model7) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
cin_s_ssp585 <- rbind(cin_s_model1,cin_s_model2,cin_s_model3,cin_s_model4,cin_s_model5,cin_s_model6,cin_s_model7)
```

srh_lm1km


``` {r, eval = FALSE}
dat_array <- ncvar_get(dat_nc, "srh_lm1km")

dat_array2 <- dat_array[,,1,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[1]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_lm1km_model1 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_lm1km_model1) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,2,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[2]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_lm1km_model2 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_lm1km_model2) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,3,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[3]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_lm1km_model3 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_lm1km_model3) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,4,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[4]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_lm1km_model4 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_lm1km_model4) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,5,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[5]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_lm1km_model5 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_lm1km_model5) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,6,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[6]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_lm1km_model6 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_lm1km_model6) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,7,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[7]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_lm1km_model7 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_lm1km_model7) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
srh_lm1km_ssp585 <- rbind(srh_lm1km_model1,srh_lm1km_model2,srh_lm1km_model3,srh_lm1km_model4,srh_lm1km_model5,srh_lm1km_model6,srh_lm1km_model7)
```

srh_lm3km


``` {r, eval = FALSE}
dat_array <- ncvar_get(dat_nc, "srh_lm3km")

dat_array2 <- dat_array[,,1,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[1]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_lm3km_model1 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_lm3km_model1) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,2,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[2]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_lm3km_model2 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_lm3km_model2) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,3,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[3]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_lm3km_model3 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_lm3km_model3) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,4,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[4]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_lm3km_model4 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_lm3km_model4) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,5,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[5]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_lm3km_model5 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_lm3km_model5) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,6,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[6]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_lm3km_model6 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_lm3km_model6) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,7,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[7]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_lm3km_model7 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_lm3km_model7) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
srh_lm3km_ssp585 <- rbind(srh_lm3km_model1,srh_lm3km_model2,srh_lm3km_model3,srh_lm3km_model4,srh_lm3km_model5,srh_lm3km_model6,srh_lm3km_model7)
```

srh_rm3km


``` {r, eval = FALSE}
dat_array <- ncvar_get(dat_nc, "srh_rm3km")

dat_array2 <- dat_array[,,1,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[1]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_rm3km_model1 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_rm3km_model1) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,2,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[2]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_rm3km_model2 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_rm3km_model2) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,3,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[3]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_rm3km_model3 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_rm3km_model3) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,4,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[4]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_rm3km_model4 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_rm3km_model4) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,5,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[5]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_rm3km_model5 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_rm3km_model5) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,6,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[6]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_rm3km_model6 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_rm3km_model6) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,7,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[7]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_rm3km_model7 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_rm3km_model7) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
srh_rm3km_ssp585 <- rbind(srh_rm3km_model1,srh_rm3km_model2,srh_rm3km_model3,srh_rm3km_model4,srh_rm3km_model5,srh_rm3km_model6,srh_rm3km_model7)
```

srh_rm1km


``` {r, eval = FALSE}
dat_array <- ncvar_get(dat_nc, "srh_rm1km")

dat_array2 <- dat_array[,,1,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[1]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_rm1km_model1 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_rm1km_model1) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,2,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[2]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_rm1km_model2 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_rm1km_model2) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,3,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[3]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_rm1km_model3 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_rm1km_model3) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,4,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[4]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_rm1km_model4 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_rm1km_model4) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,5,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[5]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_rm1km_model5 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_rm1km_model5) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,6,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[6]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_rm1km_model6 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_rm1km_model6) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
dat_array2 <- dat_array[,,7,]

 

dat_long <- as.vector(dat_array2)

nlon= (dim(lons))
nlat = dim(lats)
ntime = dim(time_stamp)
nmodels = dim(model)

dat_mat = matrix(dat_long, nrow = nlon * nlat, ncol = ntime)

lonlat <- as.matrix(expand.grid(lons,lats))
dat.df <- data.frame(cbind(lonlat,dat_mat))

modname <- model[7]
model_name = as.data.frame(rep(modname, dim(dat.df)[1]))
srh_rm1km_model7 <- cbind(dat.df,model_name)

x <- c(timestamps)
colnames(srh_rm1km_model7) <- c("Lon", "Lat", x, "Model")
```

``` {r, eval = FALSE}
srh_rm1km_ssp585 <- rbind(srh_rm1km_model1,srh_rm1km_model2,srh_rm1km_model3,srh_rm1km_model4,srh_rm1km_model5,srh_rm1km_model6,srh_rm1km_model7)
```


## Create and Save RData Files

``` {r, eval = FALSE}
#save(CAPE_ml500_historical, CAPE_s_historical, cin_ml500_historical, cin_s_historical, PRC_historical, S06_historical, srh_lm1km_historical, srh_lm3km_historical, srh_rm1km_historical, srh_rm3km_historical, file = "HistoricalData.RData")

save(CAPE_ml500_ssp585, CAPE_s_ssp585, cin_ml500_ssp585, cin_s_ssp585, PRC_ssp585, S06_ssp585, srh_lm1km_ssp585, srh_lm3km_ssp585, srh_rm1km_ssp585, srh_rm3km_ssp585, file = "ssp585Data2.RData")
```

## Historical Data
``` {r, eval = FALSE}
load("HistoricalData.RData")
```

```{r, eval = FALSE}
head(PRC_historical)
```

```{r, eval = FALSE}
library(tidyr)
library(dplyr)
```

CAPE_ml500_historical
CAPE_s_historical
cin_ml500_historical
cin_s_historical
PRC_historical
S06_historical
srh_lm1km_historical
srh_lm3km_historical
srh_rm1km_historical
srh_rm3km_historical

Create an *ID* column of the Model, Latitude, and Longitude. This will be used during the pivot stage when transfer the data from wide to long format.
```{r, eval = FALSE}
PRC_historical <- PRC_historical %>%
  mutate(ID = as.factor(paste(Model,Lon,Lat)))

CAPE_ml500_historical <- CAPE_ml500_historical %>%
  mutate(ID = as.factor(paste(Model,Lon,Lat)))

CAPE_s_historical <- CAPE_s_historical %>%
  mutate(ID = as.factor(paste(Model,Lon,Lat)))

cin_ml500_historical <- cin_ml500_historical %>%
  mutate(ID = as.factor(paste(Model,Lon,Lat)))

cin_s_historical <- cin_s_historical %>%
  mutate(ID = as.factor(paste(Model,Lon,Lat)))

S06_historical <- S06_historical %>%
  mutate(ID = as.factor(paste(Model,Lon,Lat)))

srh_lm1km_historical <- srh_lm1km_historical %>%
  mutate(ID = as.factor(paste(Model,Lon,Lat)))

srh_lm3km_historical <- srh_lm3km_historical %>%
  mutate(ID = as.factor(paste(Model,Lon,Lat)))

srh_rm1km_historical <- srh_rm1km_historical %>%
  mutate(ID = as.factor(paste(Model,Lon,Lat)))

srh_rm3km_historical <- srh_rm3km_historical %>%
  mutate(ID = as.factor(paste(Model,Lon,Lat)))
```

Convert into a longer data frame and create a column called **ID_new** that includes the ID and Date. 
```{r, eval = FALSE}
PRC_historical <- PRC_historical %>% pivot_longer(cols= colnames(PRC_historical)[3:422],
                    names_to='Date',
                    values_to='prc') 

PRC_historical <- PRC_historical%>%
  mutate(ID_new = as.factor(paste(ID,Date))) %>%
  arrange("ID_new")
####################################
CAPE_ml500_historical <- CAPE_ml500_historical %>% pivot_longer(cols= colnames(CAPE_ml500_historical)[3:422],
                    names_to='Date',
                    values_to='mlcape')
CAPE_ml500_historical <- CAPE_ml500_historical %>%
  mutate(ID_new = as.factor(paste(ID,Date))) %>%
  arrange("ID_new")
#######################################
CAPE_s_historical <- CAPE_s_historical %>% pivot_longer(cols= colnames(CAPE_s_historical)[3:422],
                    names_to='Date',
                    values_to='sfcape')
CAPE_s_historical <- CAPE_s_historical %>%
  mutate(ID_new = as.factor(paste(ID,Date))) %>%
  arrange("ID_new")
#################################
cin_ml500_historical <- cin_ml500_historical %>% pivot_longer(cols= colnames(cin_ml500_historical)[3:422],
                    names_to='Date',
                    values_to='mlcin')
cin_ml500_historical <- cin_ml500_historical %>%
  mutate(ID_new = as.factor(paste(ID,Date))) %>%
  arrange("ID_new")
#####################################
cin_s_historical <- cin_s_historical %>% pivot_longer(cols= colnames(cin_s_historical)[3:422],
                    names_to='Date',
                    values_to='sfcin')

cin_s_historical <- cin_s_historical %>%
  mutate(ID_new = as.factor(paste(ID,Date))) %>%
  arrange("ID_new")
#########################################
S06_historical <- S06_historical %>% pivot_longer(cols= colnames(S06_historical)[3:422],
                    names_to='Date',
                    values_to='shear0_6')

S06_historical <- S06_historical %>%
  mutate(ID_new = as.factor(paste(ID,Date))) %>%
  arrange("ID_new")
###################################
srh_lm1km_historical <- srh_lm1km_historical %>% pivot_longer(cols= colnames(srh_lm1km_historical)[3:422],
                    names_to='Date',
                    values_to='SRH_LM1km')

srh_lm1km_historical <- srh_lm1km_historical %>%
  mutate(ID_new = as.factor(paste(ID,Date))) %>%
  arrange("ID_new")
#################################
srh_lm3km_historical <- srh_lm3km_historical %>% pivot_longer(cols= colnames(srh_lm3km_historical)[3:422],
                    names_to='Date',
                    values_to='SRH_LM3km')

srh_lm3km_historical <- srh_lm3km_historical %>%
  mutate(ID_new = as.factor(paste(ID,Date))) %>%
  arrange("ID_new")
########################################
srh_rm1km_historical <- srh_rm1km_historical %>% pivot_longer(cols= colnames(srh_rm1km_historical)[3:422],
                    names_to='Date',
                    values_to='SRH_RM1km')

srh_rm1km_historical <- srh_rm1km_historical %>%
  mutate(ID_new = as.factor(paste(ID,Date))) %>%
  arrange("ID_new")

######################
srh_rm3km_historical <- srh_rm3km_historical %>% pivot_longer(cols= colnames(srh_rm3km_historical)[3:422],
                    names_to='Date',
                    values_to='SRH_RM3km')

srh_rm3km_historical <- srh_rm3km_historical%>%
  mutate(ID_new = as.factor(paste(ID,Date))) %>%
  arrange("ID_new")
```

Merge the data frames together. 
```{r, eval = FALSE}
CAPEs <- CAPE_s_historical %>%
  select(ID_new, sfcape)

test <- merge(CAPE_ml500_historical, CAPEs, by = "ID_new", all.x = TRUE, all.y = FALSE)


CINml <- cin_ml500_historical %>%
  select(ID_new, mlcin)

test <- merge(test, CINml, by = "ID_new", all.x = TRUE, all.y = FALSE)
########################
CINs <- cin_s_historical %>%
  select(ID_new, sfcin)

test <- merge(test, CINs, by = "ID_new", all.x = TRUE, all.y = FALSE)
########################

PRC <-PRC_historical %>%
  select(ID_new, prc)

test <- merge(test, PRC, by = "ID_new", all.x = TRUE, all.y = FALSE)
#########################
S06 <- S06_historical %>%
  select(ID_new, shear0_6)
test <- merge(test, S06, by = "ID_new", all.x = TRUE, all.y = FALSE)
##########################

SRHL1 <- srh_lm1km_historical %>%
  select(ID_new, SRH_LM1km)

test <- merge(test, SRHL1, by = "ID_new", all.x = TRUE, all.y = FALSE)
##########################

SRHL3 <- srh_lm3km_historical %>%
  select(ID_new, SRH_LM3km)

test <- merge(test, SRHL3, by = "ID_new", all.x = TRUE, all.y = FALSE)
##########################

SRHR1 <- srh_rm1km_historical %>%
  select(ID_new, SRH_RM1km)

test <- merge(test, SRHR1, by = "ID_new", all.x = TRUE, all.y = FALSE)
##########################

SRHR3 <- srh_rm3km_historical %>%
  select(ID_new, SRH_RM3km)

test <- merge(test, SRHR3, by = "ID_new", all.x = TRUE, all.y = FALSE)
```

```{r}
library(lubridate)

historical.df <- historical.df %>% 
  mutate(Year = year(Date),
         Month = month(Date))
```

```{r, eval = FALSE}
#save(historical.df, file = "Historical_CMIP6.RData")
```


## SSP585 Data
```{r, eval = FALSE}
load("ssp585Data.RData")
```

Create an *ID* column of the Model, Latitude, and Longitude. This will be used during the pivot stage when transfer the data from wide to long format. 
```{r, eval = FALSE}
PRC_ssp585 <- PRC_ssp585 %>%
  mutate(ID = as.factor(paste(Model,Lon,Lat)))

CAPE_ml500_ssp585 <- CAPE_ml500_ssp585 %>%
  mutate(ID = as.factor(paste(Model,Lon,Lat)))

CAPE_s_ssp585 <- CAPE_s_ssp585 %>%
  mutate(ID = as.factor(paste(Model,Lon,Lat)))

cin_ml500_ssp585 <- cin_ml500_ssp585 %>%
  mutate(ID = as.factor(paste(Model,Lon,Lat)))

cin_s_ssp585 <- cin_s_ssp585 %>%
  mutate(ID = as.factor(paste(Model,Lon,Lat)))

S06_ssp585 <- S06_ssp585 %>%
  mutate(ID = as.factor(paste(Model,Lon,Lat)))

srh_lm1km_ssp585 <- srh_lm1km_ssp585 %>%
  mutate(ID = as.factor(paste(Model,Lon,Lat)))

srh_lm3km_ssp585 <- srh_lm3km_ssp585 %>%
  mutate(ID = as.factor(paste(Model,Lon,Lat)))

srh_rm1km_ssp585 <- srh_rm1km_ssp585 %>%
  mutate(ID = as.factor(paste(Model,Lon,Lat)))

srh_rm3km_ssp585 <- srh_rm3km_ssp585 %>%
  mutate(ID = as.factor(paste(Model,Lon,Lat)))
```

Convert into a longer data frame and create a column called **ID_new** that includes the ID and Date. 
```{r, eval = FALSE}
PRC_ssp585 <- PRC_ssp585 %>% pivot_longer(cols= colnames(PRC_ssp585)[3:1034],
                    names_to='Date',
                    values_to='prc') 

PRC_ssp585 <- PRC_ssp585%>%
  mutate(ID_new = as.factor(paste(ID,Date))) %>%
  arrange("ID_new")
####################################
CAPE_ml500_ssp585 <- CAPE_ml500_ssp585 %>% pivot_longer(cols= colnames(CAPE_ml500_ssp585)[3:1034],
                    names_to='Date',
                    values_to='mlcape')
CAPE_ml500_ssp585 <- CAPE_ml500_ssp585 %>%
  mutate(ID_new = as.factor(paste(ID,Date))) %>%
  arrange("ID_new")
#######################################
CAPE_s_ssp585 <- CAPE_s_ssp585 %>% pivot_longer(cols= colnames(CAPE_s_ssp585)[3:1034],
                    names_to='Date',
                    values_to='sfcape')
CAPE_s_ssp585 <- CAPE_s_ssp585 %>%
  mutate(ID_new = as.factor(paste(ID,Date))) %>%
  arrange("ID_new")
#################################
cin_ml500_ssp585 <- cin_ml500_ssp585 %>% pivot_longer(cols= colnames(cin_ml500_ssp585)[3:1034],
                    names_to='Date',
                    values_to='mlcin')
cin_ml500_ssp585 <- cin_ml500_ssp585 %>%
  mutate(ID_new = as.factor(paste(ID,Date))) %>%
  arrange("ID_new")
#####################################
cin_s_ssp585 <- cin_s_ssp585 %>% pivot_longer(cols= colnames(cin_s_ssp585)[3:1034],
                    names_to='Date',
                    values_to='sfcin')

cin_s_ssp585 <- cin_s_ssp585 %>%
  mutate(ID_new = as.factor(paste(ID,Date))) %>%
  arrange("ID_new")

#########################################
S06_ssp585 <- S06_ssp585 %>% pivot_longer(cols= colnames(S06_ssp585)[3:1034],
                    names_to='Date',
                    values_to='shear0_6')

S06_ssp585 <- S06_ssp585 %>%
  mutate(ID_new = as.factor(paste(ID,Date))) %>%
  arrange("ID_new")
###################################
srh_lm1km_ssp585 <- srh_lm1km_ssp585 %>% pivot_longer(cols= colnames(srh_lm1km_ssp585)[3:1034],
                    names_to='Date',
                    values_to='SRH_LM1km')

srh_lm1km_ssp585 <- srh_lm1km_ssp585 %>%
  mutate(ID_new = as.factor(paste(ID,Date))) %>%
  arrange("ID_new")
#################################
srh_lm3km_ssp585 <- srh_lm3km_ssp585 %>% pivot_longer(cols= colnames(srh_lm3km_ssp585)[3:1034],
                    names_to='Date',
                    values_to='SRH_LM3km')

srh_lm3km_ssp585 <- srh_lm3km_ssp585 %>%
  mutate(ID_new = as.factor(paste(ID,Date))) %>%
  arrange("ID_new")
########################################
srh_rm1km_ssp585 <- srh_rm1km_ssp585 %>% pivot_longer(cols= colnames(srh_rm1km_ssp585)[3:1034],
                    names_to='Date',
                    values_to='SRH_RM1km')

srh_rm1km_ssp585 <- srh_rm1km_ssp585 %>%
  mutate(ID_new = as.factor(paste(ID,Date))) %>%
  arrange("ID_new")

######################
srh_rm3km_ssp585 <- srh_rm3km_ssp585 %>% pivot_longer(cols= colnames(srh_rm3km_ssp585)[3:1034],
                    names_to='Date',
                    values_to='SRH_RM3km')

srh_rm3km_ssp585 <- srh_rm3km_ssp585%>%
  mutate(ID_new = as.factor(paste(ID,Date))) %>%
  arrange("ID_new")
```

Merge the data frames together. 
```{r, eval = FALSE}
CAPEs <- CAPE_s_ssp585 %>%
  select(ID_new, sfcape)

test <- merge(CAPE_ml500_ssp585, CAPEs, by = "ID_new", all.x = TRUE, all.y = FALSE)


CINml <- cin_ml500_ssp585 %>%
  select(ID_new, mlcin)

test <- merge(test, CINml, by = "ID_new", all.x = TRUE, all.y = FALSE)
########################
CINs <- cin_s_ssp585 %>%
  select(ID_new, sfcin)

test <- merge(test, CINs, by = "ID_new", all.x = TRUE, all.y = FALSE)
########################

PRC <-PRC_ssp585 %>%
  select(ID_new, prc)

test <- merge(test, PRC, by = "ID_new", all.x = TRUE, all.y = FALSE)
#########################
S06 <- S06_ssp585 %>%
  select(ID_new, shear0_6)
test <- merge(test, S06, by = "ID_new", all.x = TRUE, all.y = FALSE)
##########################

SRHL1 <- srh_lm1km_ssp585 %>%
  select(ID_new, SRH_LM1km)

test <- merge(test, SRHL1, by = "ID_new", all.x = TRUE, all.y = FALSE)
##########################

SRHL3 <- srh_lm3km_ssp585 %>%
  select(ID_new, SRH_LM3km)

test <- merge(test, SRHL3, by = "ID_new", all.x = TRUE, all.y = FALSE)
##########################

SRHR1 <- srh_rm1km_ssp585 %>%
  select(ID_new, SRH_RM1km)

test <- merge(test, SRHR1, by = "ID_new", all.x = TRUE, all.y = FALSE)
##########################

SRHR3 <- srh_rm3km_ssp585 %>%
  select(ID_new, SRH_RM3km)

test <- merge(test, SRHR3, by = "ID_new", all.x = TRUE, all.y = FALSE)
```

```{r, eval = FALSE}
ssp585.df <- test
ssp585.df <- ssp585.df %>% 
  mutate(Year = year(Date),
         Month = month(Date))

save(ssp585.df, file = "SSP585_CMIP6.RData")
```

## Historical Data: Make it Spatial
```{r, eval = FALSE}
load("Historical_CMIP6.RData")

head(historical.df)
```

```{r, eval = FALSE}
historical.df <- st_as_sf(historical.df, coords = c("Lon", "Lat"), crs = 4326)
```


```{r, eval = FALSE}
hist_grid <- historical.df %>%
  st_make_grid(cellsize = 1, offset = c(229.5, 24.5))

hist_grid <- rep(hist_grid, 2940)
```

```{r, eval = FALSE}
historical.df <- historical.df %>%
  arrange(Model, Date, Lat2) 

historical.df <- cbind(historical.df, hist_grid)
```

```{r}
historical.df$year <- year(ymd(historical.df$Date))
historical.df$month <- month(ymd(historical.df$Date))
```

```{r, eval = FALSE}
#save(historical.df, file = "Historical_CMIP6.RData")
```



## SSP585 Data: Make it Spatial
```{r, eval = FALSE}
load("SSP585_CMIP6.RData")
```

```{r, eval = FALSE}
ssp585.df <- st_as_sf(ssp585.df, coords = c("Lon", "Lat"), crs = 4326)
```

```{r, eval = FALSE}
ssp585_grid <- ssp585.df %>%
  st_make_grid(cellsize = 1, offset = c(229.5, 24.5))

ssp585_grid <- rep(ssp585_grid, 7224)
```

```{r, eval = FALSE}
ssp585.df <- ssp585.df %>%
  arrange(Model, Date, Lat2) 

ssp585.df <- cbind(ssp585.df, hist_grid)
```

```{r}
library(lubridate)
library(dplyr)
ssp585.df$year <- year(ymd(ssp585.df$Date))
ssp585.df$month <- month(ymd(ssp585.df$Date))
```

```{r, eval = FALSE}
#save(ssp585.df, file = "SSP585_CMIP6.RData")
```